---
title: "Assignment"
author: "sn0wfree"
date: "12/16/2016"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
---


## Import Data
```{r import date}
crowdfunding<-read.csv( "forqrm.csv" ,header=1)
head(crowdfunding)
library(lmtest)
rownames(crowdfunding)<-crowdfunding$State
```

## Find Topics
### 1.Geography information

1. Geography information:found the significally different by state/by region
  + amount
  + successfull rate
  within graphy/plot
  
### 2. Factors:
  
2. factors:studying the relationship between Successful Rate and other factors:
  + Higher Eduction:pAdDeg;
  + Ginicoeff
  + average_pledged_amount_of_Grand.Total


### total regression

```{r regression}
summary(lm(crowdfunding$successful.rate~crowdfunding$GiniCoeff))#significant:0.00398
summary(lm(crowdfunding$successful.rate~crowdfunding$PovRate1))#0.231
summary(lm(crowdfunding$successful.rate~crowdfunding$Densitym2))# 0.109
summary(lm(crowdfunding$successful.rate~crowdfunding$pHigh))#bad:0.2320 
summary(lm(crowdfunding$successful.rate~crowdfunding$pBatDeg))#low:0.05511
summary(lm(crowdfunding$successful.rate~crowdfunding$pAdDeg))#significant:0.00501
summary(lm(crowdfunding$successful.rate~log(crowdfunding$average_of_goal_Grand.Total)))#bad:0.687
summary(lm(crowdfunding$successful.rate~log(crowdfunding$average_pledged_amount_of_Grand.Total)))#3.32e-06


summary(lm(crowdfunding$GiniCoeff~crowdfunding$pAdDeg))#significant:0.0353

summary(lm(lm(crowdfunding$successful.rate~crowdfunding$GiniCoeff)$residuals~crowdfunding$pAdDeg))#residuals ~ ADdeg:0.0368

summary(lm(log(crowdfunding$average_pledged_amount_of_Grand.Total)~crowdfunding$GiniCoeff))#0.02357


```

## Geography information


### Geography information-barplot or lineplot
```{r Geography information-barplot/lineplot}
par(mfrow=c(1,2) )
#barplot(crowdfunding$count_of_Grand.Total,names.arg = crowdfunding$State,col="skyblue")
barplot(crowdfunding$count_of_Grand.Total,col="orange",axes = 0,xlab = "State",,ylab="Count of Projects",main="Count of Projects by States")
barplot(crowdfunding$successful.rate,col="skyblue",axes  = 0,xlab = "State",main="Successful Rate by States",ylab="Successful Rate")
```


### Geography information-simpleplot
```{r Geography information-simpleplot}
par(mfrow=c(1,2) )

#count_of_Grand.Total
plot(crowdfunding$count_of_Grand.Total,col=crowdfunding$Region, main="Count of Project  Plot",ylab="Successful Rate",xaxt="n",xlab="State")
#axis(side=1,at=c(1,2,3,4,5,6,7,8),labels=c(crowdfunding$State))
legend("center",legend = levels(crowdfunding$Region),cex = 0.8, pch = 1,col=1:3)



#successful.rate
plot(crowdfunding$successful.rate,col=crowdfunding$Region, main="Successful Rate Plot",ylab="Successful Rate",xaxt="n",xlab="State")
#axis(side=1,at=c(1,2,3,4,5,6,7,8),labels=c(crowdfunding$State))
legend("bottomleft",legend = levels(crowdfunding$Region),cex = 0.8, pch = 1,col=1:3)



```

### Geography information-boxplot
```{r Geography information-boxplot}
par(mfrow=c(1,2))
#Boxplot for successful.rate and count_of_Grand.Total
#count_of_Grand.Total
boxplot(log(crowdfunding$count_of_Grand.Total[crowdfunding$Region=="Midwest"]),log(crowdfunding$count_of_Grand.Total[crowdfunding$Region=="Northeast"]),log(crowdfunding$count_of_Grand.Total[crowdfunding$Region=="South"]),log(crowdfunding$count_of_Grand.Total[crowdfunding$Region=="West"]),names=levels(crowdfunding$Region),main="Count of Projects BoxPlot by Region")

#successful.rate
boxplot(crowdfunding$successful.rate[crowdfunding$Region=="Midwest"],crowdfunding$successful.rate[crowdfunding$Region=="Northeast"],crowdfunding$successful.rate[crowdfunding$Region=="South"],crowdfunding$successful.rate[crowdfunding$Region=="West"],names=levels(crowdfunding$Region),main="Successful Rate BoxPlot by Region")





```


### Geography information-t.test
```{r Geography information-t.test}
#t.test(crowdfunding$successful.rate[crowdfunding$Region=="West"],crowdfunding$successful.rate[crowdfunding$Region=="Northeast"])
#t.test(crowdfunding$count_of_Grand.Total[crowdfunding$Region=="West"],crowdfunding$count_of_Grand.Total[crowdfunding$Region=="Northeast"])


#calcualte P Value in the t.test of Successful Rate by Region 

p=NULL
temp<-NULL
for (location1 in c(levels(crowdfunding$Region))){
  for (location2 in c(levels(crowdfunding$Region))){
    if (1){
      temp<-t.test(crowdfunding$successful.rate[crowdfunding$Region==location1],crowdfunding$successful.rate[crowdfunding$Region==location2])
      if(temp$p.value<=0.1){
        #print(c(location1,location2,temp$p.value))
      }
      p<-c(p,temp$p.value)}}}
SR.t.test.p.vlaue<-as.data.frame(matrix(p,4,4),row.names = c(levels(crowdfunding$Region)))
colnames(SR.t.test.p.vlaue)<-c(levels(crowdfunding$Region))
print("Successful Rate by Region")
SR.t.test.p.vlaue
#--------------------------------------------------------
#calcualte P Value in the t.test of Count of projects by Region 

p=NULL
temp<-NULL
for (location1 in c(levels(crowdfunding$Region))){
  for (location2 in c(levels(crowdfunding$Region))){
    if (1){
      temp<-t.test(log(crowdfunding$count_of_Grand.Total[crowdfunding$Region==location1]),log(crowdfunding$count_of_Grand.Total[crowdfunding$Region==location2]))
      if(temp$p.value<=0.1){
        #print(c(location1,location2,temp$p.value))
      }
      p<-c(p,temp$p.value)}}}
CP.t.test.p.vlaue<-as.data.frame(matrix(p,4,4),row.names = c(levels(crowdfunding$Region)))
colnames(CP.t.test.p.vlaue)<-c(levels(crowdfunding$Region))
print("Count of Projects by Region ")
CP.t.test.p.vlaue
#--------------------------------------------------------



```


```{r boxplot for variables}

boxplot(crowdfunding$successful.rate,crowdfunding$GiniCoeff,crowdfunding$pAdDeg,log(crowdfunding$average_pledged_amount_of_Grand.Total),names = c("Successful Rate","GiniCoeff","Higher Education","Average Pledged Amount"),col="skyblue")

```




```{r kmeans}
hc<-hclust(dist(crowdfunding),method = "ward.D", members = NULL)
plclust(hc)
rect.hclust(hc,k=3)




heatmap(as.matrix(dist(crowdfunding,method= 'euclidean')),labRow = F, labCol = F)
result<-cutree(hc,k=3)
as.data.frame(result)
pie(result)
barplot(result,col = "blue")
#table(result)
#summary(result)
plot(result,type = "p")


library(ggplot2)
mds2 <- -cmdscale(dist(crowdfunding))
plot(mds2, type="n", axes=FALSE, ann=FALSE)
text(mds2, labels=rownames(mds2), xpd = NA)

mds<-cmdscale(dist(crowdfunding),k=3,eig=T)
x = mds$points[,1]
y = mds$points[,2]
p=ggplot(data.frame(x,y),aes(x,y))
p+geom_point(size=5 , alpha=0.8 , aes(colour=factor(result) ))
k2<-kmeans(all,centers=5,nstart=10)
summary(k2)

```









```{r scatterplot}
library(car)
scatterplot(crowdfunding$successful.rate,log(crowdfunding$average_of_goal_Grand.Total),pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$GiniCoeff,pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$PovRate1,pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$Densitym2,pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$pHigh,pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$pBatDeg,pch=19)
scatterplot(crowdfunding$successful.rate~crowdfunding$pAdDeg,pch=19)


```

```{r rate-PovRate1}


#redo scatterplot with Successful Rate-PovRate1
scatterplot(crowdfunding$successful.rate,crowdfunding$PovRate1,pch=19)

boxplot(crowdfunding$successful.rate,crowdfunding$PovRate1,names=c("Successful Rate","PovRate1"))

ggplot(crowdfunding,aes(x=successful.rate,y=PovRate1,main = "Successful rate~PovRate"))+geom_point(aes(col=Region))+geom_smooth(method = "loess")

boxplot(crowdfunding$successful.rate[crowdfunding$PovRate1>mean(crowdfunding$PovRate1)],crowdfunding$successful.rate[crowdfunding$PovRate1<=mean(crowdfunding$PovRate1)],col = c("green","deepskyblue"),names=c("Successful%(High PovRate)","Successful%(Low PovRate)"),xlab="Successful rate by PovRate1")



t.test(crowdfunding$successful.rate[crowdfunding$PovRate1>mean(crowdfunding$PovRate1)],crowdfunding$successful.rate[crowdfunding$PovRate1<=mean(crowdfunding$PovRate1)])

par(mfrow=c(1,2))

plot(crowdfunding$successful.rate,crowdfunding$PovRate1,pch=16,col=crowdfunding$Region,xlab="Successful Rate",ylab="PovRate1",main="Successful Rate-PovRate1 Plot with lowess line")
points(lowess(crowdfunding$successful.rate,crowdfunding$PovRate1,f=1/3),pch=4,col="blue",type="l")
#abline(lm(crowdfunding$successful.rate~crowdfunding$PovRate1),col="orange")

qqplot(crowdfunding$successful.rate,crowdfunding$PovRate1,pch=13,col="orange",main="QQ plot: (Successful Rate & PovRate)",)




qqnorm(crowdfunding$successful.rate,col="orange",xlab="Successful Rate")
qqline(crowdfunding$successful.rate,col="red")
qqnorm(crowdfunding$PovRate1,col="deepskyblue",pch=18,xlab ="PovRate1")
qqline(crowdfunding$PovRate1,col="red")
```






```{r rate-Ginicoef}

ggplot(crowdfunding,aes(x=successful.rate,y=GiniCoeff,main = "Successful rate~GiniCoeff"))+geom_point(aes(col=Region))+geom_smooth(method = "loess")

boxplot(crowdfunding$successful.rate[crowdfunding$GiniCoeff>mean(crowdfunding$GiniCoeff)],crowdfunding$successful.rate[crowdfunding$GiniCoeff<=mean(crowdfunding$GiniCoeff)],col = c("darkorchid2","dodgerblue"),names=c("Successful%(High GiniCoeff)","Successful%(Low GiniCoeff)"),xlab="Successful rate by GiniCoeff")





t.test(crowdfunding$successful.rate[crowdfunding$GiniCoeff>mean(crowdfunding$GiniCoeff)],crowdfunding$successful.rate[crowdfunding$GiniCoeff<=mean(crowdfunding$GiniCoeff)])

par(mfrow=c(1,2))
plot(crowdfunding$successful.rate,crowdfunding$GiniCoeff,f=1/3 ,pch=19,col="blue",xlab="Successful Rate",ylab="GiniCoeff",main="Successful Rate-GiniCoeff Plot with lowess line")
points(lowess(crowdfunding$successful.rate,crowdfunding$GiniCoeff,f=1/3),pch=4,col="red",type="l")


qqplot(crowdfunding$successful.rate,crowdfunding$GiniCoeff,pch=19,col="red",main="Q-Q Plot: Successful Rate-GiniCoeff")


qqnorm(crowdfunding$successful.rate,col="orange",xlab="Successful Rate")
qqline(crowdfunding$successful.rate,col="red")

qqnorm(crowdfunding$GiniCoeff,col="blue",pch=20,xlab="GiniCoeff")
qqline(crowdfunding$GiniCoeff,col="red")

```






