---
title: 'Quantitative Research Methods: R_code_week 7'
author: "sn0wfree"
date: "11/10/2016"
output:
  html_document:
    toc: yes
  pdf_document:
    latex_engine: xelatex
    toc: yes
---
#Quantitative Research Methods:R_Code_week 7

*coding=UTF8*

##Import the data

```{r import_data, highlight=TRUE,echo=TRUE}
#*coding==UTF8*
#dataset=attendSLIM.xls
#attendSLIM=read.table(pipe("pbpaste"),header=TRUE)
attendSLIM=read.csv("/Users/sn0wfree/Dropbox/PhD_1st_study/BST215_Quantitative_Research_Methods_Term_1/r_code/R_code-week7/attendSLIM.csv",header=TRUE)
head(attendSLIM)
#attach(attend)
#par(mfrow=c(4,4)) #outframe set to 4*4 
```

```{r boxplot}
boxplot(attendSLIM$attendPC,attendSLIM$hwPC)
```

##t-test and the related tests

t-test use to test the small sample(n<30), it is a method to test the different of the mean between two small sampl-size data.
it use the T-dsitribution to estimate/predict the probability of difference among two samples, and evaluate the whether exist the significant difference between two mean.


###two-tail test
```{r t.test-two_tails.test}
t.test(attendSLIM$attendPC, attendSLIM$hwPC) #normal t-test 
t.test(attendSLIM$attendPC, attendSLIM$hwPC, var.equal = TRUE) #t-test with var as equal # deprecated
t.test(attendSLIM$attendPC,attendSLIM$hwPC, paired = TRUE)#pair two sample to test whether the means are equal
```
###one-tail test
mu show the true mean
```{r t.test-one_tail.test}
t.test(attendSLIM$attendPC) #test mu =0:mu show the ture mean in this one sample t-test
t.test(attendSLIM$attendPC, mu =85) #test mu=85:mu show the ture mean in this one sample t-test
t.test(attendSLIM$attendPC-85) # equivalent of t.test(attendSLIM$attendPC, mu =85) 

t.test(attendSLIM$attendPC, mu =85, alternative = "less")# one tail test
t.test(attendSLIM$attendPC, mu =82.99312)
t.test(attendSLIM$attendPC, mu =81.70956)
```


##Redo with another test: wilcox.test
the different of t-test and Wilcox.test-->[t-test and wilcox.test](http://www.zilhua.com/1118.html)<--Warning: this chinese website
the data samples are independent if they come from distinct populations and the samples do not affect each other. 
Using the Mann-Whitney-Wilcoxon Test, we can decide whether the population distributions are identical without assuming them to follow the normal distribution.

```{r wilcox.test}
wilcox.test(attendSLIM$attendPC,attendSLIM$hwPC, paired = 1) #1 means TRUE here
wilcox.test(attendSLIM$attendPC, mu =85)
```

###plot and show the chisq.test 
```{r plot_graph}
hist(table(attendSLIM$final))
hist((attendSLIM$final))#?
table(attendSLIM$final>=25)
table(attendSLIM$final>=25,attendSLIM$year)
chisq.test(table(attendSLIM$final>=25,attendSLIM$year))
```
###example tables and data for rank

####table original

original|blue|black|black blue |sum
-------|-----|-----|----------|----
M      | 20 | 30 | 70 | 120
F      | 10 | 30 | 50 | 90
-------|-----|-----|----------|-----
sum    | 30   |60   |120       |210
				

####table expected
Expected|blue|black|black blue |sum
-------|-----|-----|----------|----
M      |17.14285714|34.28571429|68.57142857|120
F      |12.85714286|25.71428571|51.42857143|90
-------|-----|-----|----------|-----
sum    |   30|  60 |120       |210

				
use $chi^2$ => ($\sum (o-e)^2$) to test different			
degree of freedom:(row-1)(column-1)		

and Hypothesis:
h1: pass rate different between year and 
h0: pass rate same between year and 


##(simple) linear Regression model
lm for linear model
1st: the simple regression on final to act

For exmaple
$final=a+b*ACT$
hypothesis: 
H0: ACT can not predict the final:$b=0$
H1: ACT can predict the final:$b!=0$

```{r simple_regression}
m1<-lm(attendSLIM$final~attendSLIM$ACT)
summary(m1)
```




## Correlation test
```{r cor.test}
cor.test(attendSLIM$final,attendSLIM$ACT)
```


## Draw the graph: residuals
```{r Image_simple_regression, include=FALSE}
boxplot(m1$residuals)
hist(m1$residuals)
qqnorm(m1$residuals)
```










